---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ActiPro

The goal of ActiPro is to provide a free and easy-to-use accelerometer processing code specifically for studies using
sensors in tandem with smartphone surveys (i.e., ecological momentary assessment). Actipro started a side project on
Stata in 2012 and has since evolved to include novel paramters of physical actvitiy that show promise in energy-balance
behavior research.

## Installation

You can install ActiPro from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("eldinidle/ActiPro")
```

## Example

You will need your own folder with AGD files to run basic sample code. As such, we currently do not have any available
examples to run. The code itself, however, is straightforward. 

```{r example}
## basic example code
```
